SIG Proceedings Paper in LaTeX Format

### 2019-08-27 SAC/submission/ACM_SigConf_SAC2020-2020_1.0/includes/contribution.tex
start word freq distribution

\subsubsection{Loss function}
Summing the matrix $S$ and multiplying it with $-1$ (to make the problem a minimizing problem) results in the loss for our entire batch. As some words may appear more than once in the batch this will more be an average of it than as with Mikolov et al. \cite{mikolov2} the exact update per pair. \\
L = $- \sum_{(i,j) \in k \times n} S(i,j) $\\

@@

>>>>

\subsubsection{Loss function}
Summing the matrix $S$ and multiplying it with $-1$ (to make the problem a minimizing problem) results in the loss for our entire batch. As some words may appear more than once in the batch this will more be an average of it than as with Mikolov et al. \citep{mikolov2} the exact update per pair. \\
L = $- \sum_{(i,j) \in k \times n} S(i,j) $\\

@@

\subsection{Distribution of word frequencies}
To tune the batch size and create batches of better quality we chose to analyze the distribution of word frequencies. A box plot of the distribution, on the text8 dataset, can be found in Figure \ref{fig:boxplot_freq}. 
\begin{figure}[h]
\centering
\includegraphics[scale=0.3]{images/boxplot_freq}
\caption{Distribution of word frequencies in the text8 datasedt}
\label{fig:boxplot_freq}
\end{figure} 
This shows that very few words are responsible for the majority of the context pairs. For example the word \textit{the} creates 50\% of the pairs in the text8 dataset. Therefore if we create batches, the word the will appear multiple time and the learning will be hindered.
